---
title: "FUSION sanity check"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r}
library("devtools")
library("ggplot2")
library("dplyr")
devtools::load_all("../../eQTLUtils/")
```

# Load permutation summary statistics from FUSION and TwinsUK datasets
```{r}
adipose = importQTLtoolsTable("../results/FUSION/FUSION.adipose_naive_ge_adipose_naive.permuted.txt.gz")
muscle = importQTLtoolsTable("../results/FUSION/FUSION.muscle_naive_ge_muscle_naive.permuted.txt.gz")
twinsuk_adipose = importQTLtoolsTable("../results/FUSION/TwinsUK_ge_fat.permuted.txt.gz")
```

# Count the number of unique genes
```{r}
nrow(adipose)
nrow(muscle)
nrow(twinsuk_adipose)
```

FUSION has many more expressed genes compared to TwinsUK. Are we completely sure that the new normalisation script uses exactly the same TPM and gene type filters (e.g. no pseudogenes)?

# Count the number of eQTLs
```{r}
dplyr::filter(muscle, p_fdr < 0.05) %>% nrow()
dplyr::filter(adipose, p_fdr < 0.05) %>% nrow()
dplyr::filter(twinsuk_adipose, p_fdr < 0.05) %>% nrow()
```
Number of eQTLs seems roughly comparable, given the there are so many more genes in FUSION dataset.

# Look at pvalue histograms
## FUSION adipose
```{r}
hist(adipose$p_beta)
```

## TwinsUK adipose
```{r}
hist(twinsuk_adipose$p_beta)
```

Both of these look normal to me.

# Make scatter plots of minimal eQTL pvalues
## Muscle vs adipose
```{r}
a = dplyr::left_join(adipose, muscle, by = "group_id")
ggplot(a, aes(x = -log(p_beta.x,10), y = -log(p_beta.y,10))) + geom_point()
```

## TwinsuK vs Fusion
Both studies profiled adipose tissue
```{r}
a = dplyr::left_join(adipose, twinsuk_adipose, by = "group_id")
ggplot(a, aes(x = -log(p_beta.x,10), y = -log(p_beta.y,10))) + geom_point()
```


